\section{Quality Attributes}

\subsection{Performance}
A computer system must always be performing, reliable, and provide consistent results. To achieve this:

\begin{itemize}
\itemsep0em 
    \item The database will be normalized to reduce data redundancy and optimize query performance.
    \item Images, graphics, and assets used within our platform will be optimized.
    \item Proper algorithms will be developed and utilized within our system.
\end{itemize}

\subsection{Usability}
The system users may not have experience with software platforms or use ones with limited functionalities. Thus, the system should be user-friendly:

\begin{itemize}
\itemsep0em 
    \item The user interface will be simple and uncluttered, designed to make it easy to find required services.
    \item Basic IT and English knowledge will be sufficient to operate the system.
    \item User interfaces will have minimal but clear designs.
    \item Functionalities will include proper validations and notifications.
\end{itemize}

\subsection{Security}
Security is paramount for user trust and data protection. The following measures will be taken:

\begin{itemize}
\itemsep0em 
    \item Guide and rental shop sign-ups and listings will be verified through relevant documents, such as endorsements and certifications.
    \item Access to the system for guides and rental services will require admin approval.
    \item Countermeasures against SQL injections, Cross-site Scripting, CORS attacks, and other vulnerabilities will be implemented.
    \item User verification via SMS or email will be enforced during password changes.
    \item All login credentials will be hashed, and Access Control will be implemented following the Least Privilege principle.
\end{itemize}

\subsection{Maintainability}
The system's ease of maintenance and future improvements is crucial. To ensure this:

\begin{itemize}
\itemsep0em 
    \item The system follows the MVC architecture, allowing the addition of new features without changing the entire system's layout.
    \item Best practices and standards will be followed throughout development.
    \item Proper developer documentation and comments will be maintained for future reference.
\end{itemize}
