\section{Introduction}
\subsection{Executive Summary}

Travelling in Sri Lanka is an enchanting experience that offers every traveller an array of captivating attractions. The most significant problem for travellers is finding the travelling and camping equipment they need. If they are camping for a few days they would need transport services, tents, cooking equipment, sleeping bags, backpacks, cameras, and such equipment to fulfil their needs during the camping period. Currently, either travellers borrow them from someone or buy them as a necessity. On the other hand, some travellers tend to hire guides for convenience.  From our project, we make this process easier by implementing an online platform that connects travellers and lessors, and travellers and guides together as well as sharing travel blogs. 		

\subsection{Problem Statement}
Sri Lanka is a beautiful country with many picturesque tourist attractions equally for local and international tourists. Camping and hiking are one of such activities. But one of the most prominent issues these hikers and campers face is searching for the exact necessary equipment. Significantly, the rural destinations don’t have many shops. And buying these equipment, only to use them rarely is a waste of money and effort. Even when finding guides, it’s hard to find someone reliable without having a prior association.


\subsection{About the Project}
In today's fast-paced world, camping and hiking have become popular activities for adventure enthusiasts and nature lovers in Sri Lanka. However, planning these can be a drag, with most arrangements being made offline, leading to time-consuming searches and uncertainty. Recognizing the need for a more streamlined approach, we present our innovative Camping Equipment Rental and Guidance Platform.

We understand that finding the right equipment is crucial for any outdoor journey. To address this, we have thoughtfully classified the relevant shops based on their destinations, allowing you to easily access all the necessary camping gear in one place. Whether you are planning a local hike or an international camping trip, our platform will be your trusted companion throughout the process.

One of the primary concerns for campers and hikers is the ability to locate suitable equipment near their living area, destination, or on route. Our platform eliminates this issue by providing you with a user-friendly interface that allows you to discover camping equipment rental options conveniently. With just a few clicks, you can view a comprehensive list of rental services available in your desired location, making the planning process a breeze.

Moreover, our platform caters to the needs of those seeking guidance and know-how for their outdoor endeavours. Reliable guides are an integral part of our ecosystem, ensuring that you have access to valuable insights and expert advice throughout your journey. We also pride ourselves on incorporating a review system, providing customers with essential feedback to make informed decisions when selecting guides.


\subsection{How Is It Different?}
\begin{enumerate}
    \item Reliable Guides: We ensure only trusted and qualified guides are available, guaranteeing a safe and enjoyable outdoor experience. Also, the guides can make a customer base through this system.
    \item Rental Services and Guidance All in One: We bring camping equipment rental services and expert guides together in a single platform, simplifying the planning process. Also, rental services can make a customer base through this system.
    \item Review System: Our transparent review system empowers users to provide feedback, promoting accountability and helping others make informed decisions. Only the users who went on a journey with a particular Guide, have access to review them.
    \item Blog: Users can write up-to-date blog content for fellow campers, and share their experiences, enhancing their knowledge in preparation. These will be approved by the admin and will be uploaded to the system. 
    \item Tips and know-how: The users can view valuable tips and know-how, best practices which will be added and updated by guides and admin, preparing them for the adventure.
    \item Efficiency and Time-saving: The digital platform eliminates the need for extensive searches, allowing users to access options and make choices efficiently.



\end{enumerate}